Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2015-10-21 draft.tex
Update to-do list. Refer to 'dynamic four-player model' in the text.

\begin{abstract}
\noindent Unrecognized states are characterized by stagnant or crumbling economies and political instability, often serve as havens for illicit trade, and challenge the territorial sovereignty of recognized states. Their persistence is both intellectually puzzling and normatively problematic, but unrecognized statehood can be a remarkably stable outcome, persisting for decades. Our four-player model reveals that unrecognized statehood emerges as an equilibrium outcome when a patron state is willing and able to persistently invest resources to sustain it. %Counterintuitively, patrons will make these investments even when unrecognized statehood is not their most preferred outcome. 
We assess options available to actors in the international community who seek to impose their preferred outcomes in these disputes and find that, although sanctions are the most frequently employed, they can often lead to renewed conflict instead of the intended resolution.
\end{abstract}

@@

We develop a four-player model that focuses on the core conflict between the home state and the secessionist elite, but also incorporates the actions of outside states with interests in the outcome. These outside actors are a patron, which prefers independence to reunification, and a fourth player we denote as player $c$ who represents one or more members of the international community. Player $c$ is assumed to prefer reunification to independence.

@@

While the importance of outside actors in civil conflict has been widely acknowledged in the empirical literature, it is rarely modeled formally. We introduce a four-player model that captures the core strategic interactions of the secessionist elite and the home state central government, as well as the interventions of outside actors with interests in the outcome. This allows us both to examine the means through which patron states sustain unrecognized statehood as a stable equilibrium, and to rigorously analyze the strategies available to other outside actors to pursue reunification. It is not always in the interests of outside states to bear the costs of inducing their preferred outcome, but we identify the mechanisms through which this is possible and the thresholds that must be overcome.

>>>>

\begin{abstract}
\noindent Unrecognized states are characterized by stagnant or crumbling economies and political instability, often serve as havens for illicit trade, and challenge the territorial sovereignty of recognized states. Their persistence is both intellectually puzzling and normatively problematic, but unrecognized statehood can be a remarkably stable outcome, persisting for decades. Our dynamic four-player model reveals that unrecognized statehood emerges as an equilibrium outcome when a patron state is willing and able to persistently invest resources to sustain it. %Counterintuitively, patrons will make these investments even when unrecognized statehood is not their most preferred outcome. 
We assess options available to actors in the international community who seek to impose their preferred outcomes in these disputes and find that, although sanctions are the most frequently employed, they can often lead to renewed conflict instead of the intended resolution.
\end{abstract}

@@

We develop a dynamic four-player model that focuses on the core conflict between the home state and the secessionist elite, but also incorporates the actions of outside states with interests in the outcome. These outside actors are a patron, which prefers independence to reunification, and a fourth player we denote as player $c$ who represents one or more members of the international community. Player $c$ is assumed to prefer reunification to independence.

@@

While the importance of outside actors in civil conflict has been widely acknowledged in the empirical literature, it is rarely modeled formally. We introduce a dynamic four-player model that captures the core strategic interactions of the secessionist elite and the home state central government, as well as the interventions of outside actors with interests in the outcome. This allows us both to examine the means through which patron states sustain unrecognized statehood as a stable equilibrium, and to rigorously analyze the strategies available to other outside actors to pursue reunification. It is not always in the interests of outside states to bear the costs of inducing their preferred outcome, but we identify the mechanisms through which this is possible and the thresholds that must be overcome.
